Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-12-08 results.tex
attempting to resize results table
still resizing results table
adding a columnwidth req to results table
shrinking results table with footnotesize
updating numbers in results table

\begin{table}[h!]
\centering
  \caption{Summary of cascades level population.}
\begin{tabular}{ccccccccc}
\toprule

Model       &        &            & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R       \\
%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed       & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.33w\%$ \\
Level 0 & Assay      & Product    & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $4.82w\%$ \\
        &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
        & Cascades   & Impl. (Ideal)& 25(26.7)  & 25(26.4)  & 25(26.6)  & 24(25.8)  & 25(26.7)  & 25(26.4)  \\
\midrule                                                                                                 
        &            & Feed       & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $12.2w\%$ \\
Level 1 & Assay      & Product    & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $58.5w\%$ \\
        &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
        & Cascades   & Impl. (Ideal)& 3(2.9)    & 4(3.2)    & 3(2.9)    & 4(3.4)    & 3(2.9)    & 4(3.2)    \\
\midrule                                                                                                 
        &            & Feed       & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $58.5w\%$ \\
Level 2 & Assay      & Product    & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $97.0w\%$ \\
        &            & Tails      & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
        & Cascades   & Impl. (Ideal)& 1(0.3)    & 1(0.3)    & 1(0.4)    & 1(0.6)    & 1(0.3)    & 1(0.35)   \\
\midrule                                                                                                 
        &            & Feed       & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product    & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   & Impl. (Ideal)& 1(0.03)   & N.A.      & 1(0.08)   & 1(0.2)    & 1(0.03)   & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

>>>>

\begin{table}[h!]
\footnotesize
\centering
  \caption{Summary of cascades level population.}
\resizebox{\columnwidth}{!}{%
\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} cccccccc}
\toprule

Model       &        &                & A/NR     & A/R      & B/NR     & B/R      & C/NR     & C/R       \\
%Recycling   &       &                & No       & Yes      & No       & Yes      & No       & Yes        \\
\midrule                                                                                                 
        &            & Feed $w\%$     & $0.71$   & $1.31$   & $0.71$   & $0.92$   & $0.71$   & $1.30$ \\
Level 0 & Assay      & Product $w\%$  & $3.97$   & $7.27$   & $3.97$   & $5.10$   & $3.97$   & $7.24$ \\
        &            & Tails $w\%$    & $0.28$   & $0.52$   & $0.28$   & $0.36$   & $0.28$   & $0.51$ \\
        & Cascades   & Impl. (Ideal)  & 25(26.5) & 25(26.5) & 25(26.4) & 24(26.3) & 25(26.5) & 25(26.2)  \\
\midrule                                                                                                 
        &            & Feed $w\%$     & $3.97$   & $11.48$  & $3.97$   & $6.29$   & $3.97$   & $11.64$ \\
Level 1 & Assay      & Product $w\%$  & $21.29$  & $53.30$  & $19.33$  & $27.98$  & $21.41$  & $55.12$ \\
        &            & Tails $w\%$    & $1.68$   & $5.93$   & $1.58$   & $2.54$   & $1.66$   & $5.88$ \\
        & Cascades   & Impl. (Ideal)  & 3(3.1)   & 4(3.1)   & 3(3.1)   & 4(3.1)   & 3(3.1)   & 4(3.4)    \\
\midrule                                                                                                 
        &            & Feed $w\%$     & $21.29$  & $53.3$   & $19.33$  & $31.09$  & $21.41$  & $55.12$ \\
Level 2 & Assay      & Product $w\%$  & $76.39$  & $94.70$  & $58.10$  & $72.31$  & $79.21$  & $96.37$ \\
        &            & Tails $w\%$    & $13.98$  & $47.81$  & $8.51$   & $14.91$  & $13.75$  & $49.65$ \\
        & Cascades   & Impl. (Ideal)  & 1(0.4)   & 1(0.4)   & 1(0.4)   & 1(0.5)   & 1(0.4)   & 1(0.4)   \\
\midrule                                                                                                 
        &            & Feed $w\%$     & $76.39$  & N.A.     & $58.10$  & $72.31$  & $79.21$  & N.A.      \\
Level 3 & Assay      & Product $w\%$  & $98.09$  & N.A.     & $88.92$  & $93.79$  & $98.86$  & N.A.      \\
        &            & Tails $w\%$    & $73.51$  & N.A.     & $35.01$  & $50.36$  & $76.60$  & N.A.      \\
        & Cascades   & Impl. (Ideal)  & 1(0.04)  & N.A.     & 1(0.09)  & 1(0.1)   & 1(0.04)  & N.A.      \\
\midrule                                                                                                 
        &            & Feed $w\%$     & N.A.     & N.A.     & $88.92$  & N.A.     & N.A.     & N.A.      \\
Level 4 & Assay      & Product $w\%$  & N.A.     & N.A.     & $97.89$  & N.A.     & N.A.     & N.A.      \\
        &            & Tails $w\%$    & N.A.     & N.A.     & $75.71$  & N.A.     & N.A.     & N.A.      \\
        & Cascades   & Impl. (Ideal)  & N.A.     & N.A.     & 1(0.04)  & N.A.     & N.A.     & N.A.      \\
\bottomrule
\end{tabular*}
}
\label{tab:level}
\end{table}
